Backbone-Store: An API for Automating Local Caching of Web Application Data

### 2012-05-21 paper/paper.tex
Fixed part about save-time characteristics

Finally, we also tested update times for our two local storage strategies. We did
this by creating collections with different numbers of items, and measuring the
time to save each collection to local storage. Also, to test different save-time
characteristics of our different persistence strategies, we measured the time
to resave the collection after adding one model. We predict that the
one-key-per-model local storage strategy will allow faster updates, by making it
possible to save only those models that were changed or added since the last
save.

>>>>

Finally, we also tested update times for our two local storage strategies, by
creating collections with different numbers of items and measuring the time to
save each collection to local storage. Also, we believe that our two strategies
will behave differently in different situations (i.e., saving an entire
collection for the first time, and saving a collection again after having
changed or added only a few models); we test this by measuring the time to
resave the collection after adding one new model. We predict that the
one-key-per-model local storage strategy will allow faster updates, by making
it possible to save only those models that were changed or added since the last
save.
